On the discovery and origin of $r$-process stars in the Milky Way

### 2018-02-07 article/ms.tex
some abs

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the LAMOST survey, more than doubling the known number in our Galaxy. To our knowledge, we provide the first estimate on whether neutron star mergers are frequent enough to account for all known r-process stars in the Milky Way. \todo{We conclude....}. \todo{The discovery of these stars implies multiple r-process sites.}
		% contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material exclusively being produced in very large amounts in very rare events, such as neutron star mergers. 
	\end{abstract}

>>>>

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in our Galaxy. After taking expected rates of core-collapse supernovae and the average r-process material ejected in each event, we find the core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work. Current rate estimates of neutron-star mergers imply that should be about $\todo{X}$ r-process enhanced stars in the Milky Way, and about $\todo{Y}$ in LAMOST DR2. \todo{conclusions....}To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
		% contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material exclusively being produced in very large amounts in very rare events, such as neutron star mergers. 
	\end{abstract}
